PAWpySeed: A parallelized Python/C package for analyzing DFT wavefunctions in the PAW formalism

### 2018-03-21 docs/paper.tex

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
\hline
Computational Task & $\Theta$ & Frequency*\\
\hline
$\widetilde{O}$ & $BKSW$ & per band\\
$O_M$ & $BKSNP$ & per band\\
$O_R$ and $O_S$ & $BKSNP$ & per band\\
$O_N$ & $BKSNP$ & per band\\
$\braket{\widetilde{p}_i|\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSF\mathrm{log}(F)$ & per structure\\
$(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
\ket{\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSNPW$ & per structure\\
spherical Bessel transform partial waves & $NPG\mathrm{log}(G)$ & per structure pair\\
project plane waves onto partial waves & $EPKW$ & per structure pair\\
projections for overlapping aug spheres & $NPL$ & per structure pair\\
\hline
\end{tabular}

\begin{tabular}{c|c}
Symbol & Definition\\
\hline
B & number of bands\\
E & number of elements\\
F & size of FFT grid\\
G & size of partial wave radial grid\\
K & number of k-points\\
L & size of Legendre-Gauss grid around ions\\
N & number of sites**\\
P & number of projector functions\\
S & number of spin states\\
W & number of plane waves\\
\end{tabular}
\caption{Runtime scaling functions for each component of the code and
definitions for shorthand symbols to express runtime.
*The frequency refers to how often the routine is called. "Per band"
indicates that the routine runs once every time a band from one structure
is projected onto all the bands of a basis structure. "Per structure"
indicates that the routine is a "setup" routine that must be called once
for each structure and corresponding band structure to do perform projections.
"Per structure pair" is the same as "per structure" except that the routine
is only run once for a pair of structures with the same lattice and plane-wave
basis set, the bands of one such structure to be used as a basis set for the other.
**Number of sites flexibly refers to the number of sites relevant to the calculation,
which worst-case scales with the total number of sites in the structure. For example,
calculating $O_M$ and $O_N$ only require the sites in sets $M$ and $N_RS$, respectively.}
\label{tab:runtime}
\end{table}

@@

\begin{enumerate}
	\item
	Settings
	\item
	adsf
	\item
	\textbf{Non local Part}: This section contains the \emph{non local projector functions}.
	The first line after "Non local Part" gives the $l$ quantum number of the projector,
	the number of projectors for that $l$ quantum number, and the radius of the real
	space projector region.
	\begin{enumerate}
		\item
		\textbf{Reciprocal Space Part}: The reciprocal space projection operator.
		\item
		\textbf{Real Space Part}: The real space projection operator values on a radial
		grid. The radius at a given index $I$ is $RMAX*I/NDATA$, where RMAX and NDATA
		are given in the settings section. Since $I$ is 0-indexed, the true maximal
		radius of the projector is actually $RMAX*(NDATA-1)/NDATA$. Unlike the
		\emph{partial wave} values (see \textbf{pseudo wavefunction},
		the projector values are not mulitplied by $r$.
		$$p(\mathbf{r})=realspacepart(index)Y_l^m(\hat{\mathbf{r}})$$
	\end{enumerate}
	\item
	PAW Radial Sets
	\begin{enumerate}
		\item
		Augmentation charges
		\item
		Occupancies
		\item
		\textbf{grid}: The exponential grid on which calculations related
		to the \emph{partial waves} are performed.
		\item
		\textbf{pseudo wavefunction}: A pseudo \emph{partial wave} on the provided
		radial grid, multiplied by $r$ for easy radial integration. I.e.
		$$\phi(\mathbf{r}(index))=\frac{pseudowavefunction(index)}{r(index)}Y_l^m(\hat{\mathbf{r}})$$
		Listed in the same order as the projector functions.
		\item
		\textbf{ae wavefunction}: Same pseudo wavefunction, but for the all electron \emph{partial wave}.
	\end{enumerate}
\end{enumerate}

>>>>

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
\hline
Computational Task & $\Theta$ & Frequency*\\
\hline
$\widetilde{O}$ & $BKSW \sim n^2$ & per band\\
$O_M$ & $BKSNP \sim n^2$ & per band\\
$O_R$ and $O_S$ & $BKSNP \sim n^2$ & per band\\
$O_N$ & $BKSNP \sim n^2$ & per band\\
$\braket{\widetilde{p}_i|\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSF\mathrm{log}(F)
\sim n^2\mathrm{log}(n)$ & per structure\\
$(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
\ket{\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSNPW \sim n^3$ & per structure\\
spherical Bessel transform partial waves & $NPG\mathrm{log}(G) \sim n$ & per structure pair\\
project plane waves onto partial waves & $EPKW \sim n$ & per structure pair\\
projections for overlapping aug spheres & $NPL \sim n$ & per structure pair\\
\hline
\end{tabular}

\begin{tabular}{c|c}
Symbol & Definition\\
\hline
B & number of bands\\
E & number of elements\\
F & size of FFT grid\\
G & size of partial wave radial grid\\
K & number of k-points\\
L & size of Legendre-Gauss grid around ions\\
N & number of sites**\\
P & number of projector functions\\
S & number of spin states\\
W & number of plane waves\\
n & number of electrons (approximate scaling)
\end{tabular}
\caption{Runtime scaling functions for each component of the code and
definitions for shorthand symbols to express runtime. Approximate
scales with the number of electrons are also shown.
*The frequency refers to how often the routine is called. "Per band"
indicates that the routine runs once every time a band from one structure
is projected onto all the bands of a basis structure. "Per structure"
indicates that the routine is a "setup" routine that must be called once
for each structure and corresponding band structure to do perform projections.
"Per structure pair" is the same as "per structure" except that the routine
is only run once for a pair of structures with the same lattice and plane-wave
basis set, the bands of one such structure to be used as a basis set for the other.
**Number of sites flexibly refers to the number of sites relevant to the calculation,
which worst-case scales with the total number of sites in the structure. For example,
calculating $O_M$ and $O_N$ only require the sites in sets $M$ and $N_RS$, respectively.}
\label{tab:runtime}
\end{table}

@@

\begin{enumerate}
	\item
	\textbf{Settings}: The parameters used for the generation of the psuedopotentials,
	as described thoroughly in VASP and pymatgen documentation.
	\item
	A bunch of stuff I still don't understand and which has no discernible grid.
	\item
	\textbf{Non local Part}: This section contains the \emph{non local projector functions}.
	The first line after "Non local Part" gives the $l$ quantum number of the projector,
	the number of projectors for that $l$ quantum number, and the radius of the real
	space projector region.
	\begin{enumerate}
		\item
		\textbf{Reciprocal Space Part}: The reciprocal space projection operator.
		\item
		\textbf{Real Space Part}: The real space projection operator values on a radial
		grid. The radius at a given index $I$ is $RMAX*I/NDATA$, where RMAX and NDATA
		are given in the settings section. Since $I$ is 0-indexed, the true maximal
		radius of the projector is actually $RMAX*(NDATA-1)/NDATA$. Unlike the
		\emph{partial wave} values (see \textbf{pseudo wavefunction},
		the projector values are not mulitplied by $r$.
		$$p(\mathbf{r})=realspacepart(index)Y_l^m(\hat{\mathbf{r}})$$
	\end{enumerate}
	\item
	\textbf{PAW Radial Sets}
	\begin{enumerate}
		\item
		Augmentation charges
		\item
		Occupancies
		\item
		\textbf{grid}: The exponential grid on which calculations related
		to the \emph{partial waves} are performed.
		\item
		\textbf{pseudo wavefunction}: A pseudo \emph{partial wave} on the provided
		radial grid, multiplied by $r$ for easy radial integration. I.e.
		$$\phi(\mathbf{r}(index))=\frac{pseudowavefunction(index)}{r(index)}Y_l^m(\hat{\mathbf{r}})$$
		Listed in the same order as the projector functions.
		\item
		\textbf{ae wavefunction}: Same pseudo wavefunction, but for the all electron \emph{partial wave}.
	\end{enumerate}
\end{enumerate}
